---
name: Henry
surname: Cho
position: "Senior Data Scientist"
#address: "School of Physics & Chemistry, École Normale Supérieure"
phone: +1 778 999 6639
#www: mariecurie.com
email: henry.cho@outlook.com
#twitter: mariecurie
#github: mariecurie
linkedin: linkedin.com/in/henrycho/
date: "`r format(Sys.time(), '%B %Y')`"
docname:  Coded and rendered in R
output: vitae::awesomecv
---


```{r setup, include=FALSE}
library(tidyverse)
library(vitae)
knitr::opts_chunk$set(echo = FALSE)
```

# Summary
Results orientated business professional with a solid background in health care, leadership, consulting, and analytics. Known for both technical and business acumen and the ability to bridge communication gaps between technical, business, and executive audiences.

# Skills  

\setlength{\parindent}{2ex}
\setlength{\parskip}{0em}
\textbullet\  Dynamic and pro-active with a sense of urgency for resolution and the ability to execute \par
\textbullet\  Experience leading projects and others in a cross functional team environment \par
\textbullet\  Ability to communicate complex insights at all levels of the organization through impactful storytelling \par
\textbullet\  Advanced knowledge of data and analytical tools such as *R*, *Python*, *SAS EG*, *SQL*, *Knime*, *PowerBI* and *Tableau* \par
\textbullet\  Solution oriented with a strong sense of ownership with an ability to make decisions and recommendations \par
\textbullet\  Adept at working with large complex datasets to develop analytical models and insights \par 

\setlength{\parindent}{0ex}
\setlength{\parskip}{1em}


# Education
```{r}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
  "Master of Business Administration", "Simon Fraser University", "BC, Canada", "2021", "Estimated Completion in December 2021",
  "Bachelor of Business Administration", "British Columbia Institute of Technology", "BC, Canada", "2014", "Major in Marketing Management and a minor in Entrepeneurship"
) %>% 
  detailed_entries(uni, dates, degree, loc, details)
```

# Experience
```{r}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
# PROVINCIAL HEALTH SERVICES AUTHORITY
  "Senior Business Analyst", 
  "Provincial Health Services Authority", 
  "Vancouver, BC", "Jan 2020 - Present", 
  "Supported business leaders by providing comprehensive, timely and high-quality reports and analysis to support operational decision-making and business planning.",

  "Senior Business Analyst", 
  "Provincial Health Services Authority", 
  "Vancouver, BC", "Jan 2020 - Present", 
  "Oversaw the development and deployment of business intelligence tools within the department using PowerBI and R and led the transition to a pull reporting model reducing redundant and recurring work by 80 percent increasing both bandwidth and transparency across the entire department.",

"Senior Business Analyst", 
  "Provincial Health Services Authority", 
  "Vancouver, BC", "Jan 2020 - Present", 
  "Successfully led and delivered multiple high priority and visibility projects to directly support the provincial Covid-19 response including the development of multiple dashboards, models and presentations.",
  
  "Senior Business Analyst", 
  "Provincial Health Services Authority", 
  "Vancouver, BC", "Jan 2020 - Present", 
  "Provided mentorship to peers in a technical capacity and directly oversaw the department’s interns including hiring, training, skills, and career development.",

"Senior Business Analyst", 
  "Provincial Health Services Authority", 
  "Vancouver, BC", "Jan 2020 - Present", 
  "Automated recurring reports and processes in R to increase the capacity within the department for higher priority and specialized work.",

"Senior Business Analyst", 
  "Provincial Health Services Authority", 
  "Vancouver, BC", "Jan 2020 - Present", 
  "Spearheaded the transition to a modern task system (Trello) in addition to spearheading the transition to a pull reporting model through the development of self-serve tools such as dashboards.",

"Senior Business Analyst", 
  "Provincial Health Services Authority", 
  "Vancouver, BC", "Jan 2020 - Present", 
  "Supported business leaders by providing comprehensive, timely and high-quality reports and analysis to support decision-making.",

"Senior Business Analyst", 
  "Provincial Health Services Authority", 
  "Vancouver, BC", "Jan 2020 - Present", 
  "Oversaw the quarterly reporting process and developed a process to ensure that all the requirements are met in a timely manner and to a high standard.",

"Senior Business Analyst", 
  "Provincial Health Services Authority", 
  "Vancouver, BC", "Jan 2020 - Present", 
  "Established close relationships with operational and business leaders to ensure successful outcomes and mutually beneficial relationships.",

"Senior Business Analyst", 
  "Provincial Health Services Authority", 
  "Vancouver, BC", "Jan 2020 - Present", 
  "A key strategic partner to the surgical program  at BC Children's and Women's hospital supporting reporting, projections and ad-hoc analysis.",

#PROVIDENCE HEALTH
"Analyst",
  "Providence Health Care",
  "Vancouver, BC",
  "Aug 2018 - Jan 2020",
  "Applied analytical, business and data management skills to achieve a comprehensive multilayered understanding of the business process.",

"Analyst",
  "Providence Health Care",
  "Vancouver, BC",
  "Aug 2018 - Jan 2020",
  "Provided application and analysis of appropriate statistical test to information as well as expert assessment of data quality and validation.",

"Analyst",
  "Providence Health Care",
  "Vancouver, BC",
  "Aug 2018 - Jan 2020",
  "Identified opportunities for improvement in the data and business processes while collaborating with stakeholders to ensure that workable pragmatic solutions are developed.", 

"Analyst",
  "Providence Health Care",
  "Vancouver, BC",
  "Aug 2018 - Jan 2020",
  "Mentored staff and leaders in the development of skills to improve their understanding of the range of analytical matters, processes, reporting and system requirements.", 

"Analyst",
  "Providence Health Care",
  "Vancouver, BC",
  "Aug 2018 - Jan 2020",
  "Collaborated with other health authorities on various site level and province wide projects with a focus on reporting and performance improvement.", 

"Analyst",
  "Providence Health Care",
  "Vancouver, BC",
  "Aug 2018 - Jan 2020",
  "Incorporated analytical, business and data management assessment skills and methodology to achieve a thorough understanding of the related analytical and business processes and tools.", 

"Analyst",
  "Providence Health Care",
  "Vancouver, BC",
  "Aug 2018 - Jan 2020",
  "Liaised with stakeholders in setting short and long-term objectives and identifying opportunities.",

# SHAW COMMUNICATIONS
"Data Analyst",
  "Shaw Communications",
  "Vancouver, BC",
  "Feb 2016 - May 2018",
  "Provided analysis of business performance and a summary of key issues and trends affecting the business",

"Data Analyst",
  "Shaw Communications",
  "Vancouver, BC",
  "Feb 2016 - May 2018",
  "Prepared forecast reports for operations and analysis of how key changes would affect our assumptions and performance.",

"Data Analyst",
  "Shaw Communications",
  "Vancouver, BC",
  "Feb 2016 - May 2018",
  "Provided forecasting and analysis using R and Excel to set performance targets with considerations to impacts to staffing and budgeting for our contact centers nationally.",

"Data Analyst",
  "Shaw Communications",
  "Vancouver, BC",
  "Feb 2016 - May 2018",
  "Provided continuous monitoring and reporting of current business performance and provided recommendations when required to ensure business objectives are met.",

"Data Analyst",
  "Shaw Communications",
  "Vancouver, BC",
  "Feb 2016 - May 2018",
  "Executed workforce and budgeting strategies to enhance operations while balancing workforce and financial restrictions.",

"Data Analyst",
  "Shaw Communications",
  "Vancouver, BC",
  "Feb 2016 - May 2018",
  "Negotiated budget and adjustments with consideration to Finance and Operations maintaining a satisfactory level of performance throughout all disciplines of the business.",

"Data Analyst",
  "Shaw Communications",
  "Vancouver, BC",
  "Feb 2016 - May 2018",
  "Managed all aspects of commission structure from performance to payouts and bonuses.",

"Data Analyst",
  "Shaw Communications",
  "Vancouver, BC",
  "Feb 2016 - May 2018",
  "Supported overall performance management by driving desired behaviours through the development and deployment of incentives."
) %>% 
  detailed_entries(company, dates, role, loc, details)
```

# Notable Projects
```{r}
tribble(
  ~ uni, ~proj, ~ loc, ~ dates, ~ details,
  "Provincial Health Services Authority",
  "BC Women's OR Slate Scheduling Model",
  "", 
  "May 2021 - August 2021",
  "Developed a model to appropriately allocate slate hours based on a variety of inputs such as waitlist size, wait time and surgeon efficiency. The model enables a standardized and transparent approach to slate allocation while providing incentives to surgeons who exhibit desired behaviours.",
  
    "Provincial Health Services Authority",
  "Provincial Vaccination Site Mapping Tool",
  "", 
  "March 2021 - March 2021",
  "Led the design and development of a tool in PowerBI which mapped all the vaccinations sites across the province to support the provincial vaccination efforts. The tool featured a provincial map with points which highlighted the community and health authority each site served as well as the site size, hours, and resourcing.",
  
  "Provincial Health Services Authority",
  "Provincial Employee Vaccinations Dashboard",
  "", 
  "February 2021 - March 2021",
  "In collaboration with the HR Informatics team, we developed a dashboard in PowerBI to monitor all employee vaccinations across the province. The tool kept track of doses by vaccine type, program completion by phase and even made predictions of how many second doses of each type of vaccine were required for each health authority.",
  
  "Provincial Health Services Authority",
  "Covid Assessments Dashboard",
  "", 
  "December 2020 - January 2021",
  "Directed the development and deployment of a dashboard developed in R to monitor Covid testing volumes across various sites. The primary focus of the tool was to identify patterns of congestion from sample collection to results across the various testing locations.",
  
  "Provincial Health Services Authority",
  "Provincial Surgical Dashboard",
  "", 
  "August 2020 - December 2020",
  "Led the design and development of a Surgical Dashboard to support the strategic surgical planning at the provincial level. The dashboard's primary focus is to improve surgical wait times by identifying problem areas and patterns within each Health Authority or Surgical Service.",

  "Provincial Health Services Authority",
  "Provincial COVID Monitoring Solution",
  "",  
"March 2020 - April 2020",
  "Led the design, development and delivery of an operational tool which kept track of COVID patients in the health care system. The tool was designed from the ground up requiring the development of data capture processes, data feeds, ETLs, and data storage. A few primary features of the tool is that it not only tracks Covid patients, but also unit occupancy and ventilator utilization. The data from this dashboard directly informs the provincial pandemic response and was developed from the ground up within a month. Snippets from this dashboard is often featured in the weekly addresses from the Provincial Health Officer.",
  
   "Providence Health Care",
  "Emergency Department Load Planning ",
  "", 
  "March 2020 - April 2020",
  "Supported the development a machine learning model to predict a patient's Length of Stay at the point of admission and to support discharge planning and the management of patient flow.",
  
  "Shaw Communications",
  "Call Center Sales Staff Employee Churn Model ",
  "", 
  "Jun 2017 - Mar 2018",
  "Supported a team of Data Scientist working to develop proactive churn models. Supported the development of the models by identifying key predictor variables through regression analysis and A/B testing.", 
  
    "Shaw Communications",
  "Pay for Performance",
  "", 
  "Sep 2016 - May 2018",
  "Manually deployed and managed an incentivized performance plan for all contact centers nationwide. Responsible for a budget of over 2.5 million dollars annually. Supported the deployment from a manual process to full end to end automation.", 
  
) %>% 
  detailed_entries(uni, dates, proj, loc, details)
```

 